### 2013-09-26 evaluation/paper.tex
move interesting phenomenon back to letters.

We start our experiments with the MNIST dataset.
The convergence of the primal suboptimality and training set loss in terms of
passes over the training set is shown in \Figref{mnist_curves}. While inference
is trivial, this is by far the largest dataset, making the $n$-slack algorithms
not feasible. We see that the stochastic algorithms are much faster than the
cutting plane algorithm, in particular initially, even in terms of iterations,
with the SZLJSP clearly leading the way.
%Interestingly, the $1$-slack algorithm
%catches up near the desired suboptimality and is faster in achieving the desired duality gap--even though
%the primal objective is always above SZLJSP\@. A zoom-in can be found in
%\Figref{ocr_small_duality}, right hand side.

We want to highlight an interesting phenomenon here: The cutting-plane algorithms stop immediately
when reaching the desired suboptimality of $0.1$. The SZLJSP algorithm, on the other hand, keeps
on learning much longer---even though the primal of the $1$-slack algorithms is
always above the primal of the SZLJSP\@. This is caused by a looser bound
given by the dual. Remember that the stopping criterion for both cutting-plane 
and SZLJSP are given by the duality gap. It seems that while the primal objective converges much
faster in the SZLJSP algorithm than in the non-caching $1$-slack algorithm, the dual does not.
This means that in this practical experiment, the non-caching $1$-slack algorithm was \emph{faster}
in guaranteeing the desired suboptimality. \Figref{ocr_small_dual} illustrates this point by plotting primal and dual
objectives for the $1$-slack cutting plane and the SZLJSP algorithms.
 Looking at the training set loss in \Figref{mnist_curves} suggests that the
 high precision we demanded was not necessary, and we could have terminated the
 stochastic algorithms much earlier.

@@

We now consider datasets with non-trivial inference.
The results for \textsc{OCR-small} are shown in \Figref{ocr_small_results}.
Considering the plot against passes over the dataset on the left, several
trends can be observed: the $n$-slack cutting plane algorithms converge
fastest, with the version that recomputes the QP at every step leading the
race. The algorithms are closely followed by the caching $1$-slack cutting
plane algorithm.  They are followed by the significantly slower SZLJSP
algorithm, and finally the non-caching $1$-slack cutting plane algorithm and
subgradient descent.  These results are intuitive, as they reflect ``how much
work'' each algorithm does for each loss-augmented prediction step. More work
towards the objective leads to faster convergence.  This ``more work'' is
quantified on the right hand side of \Figref{ocr_small_results}, where the suboptimality is plotted against time.
Clearly the $n$-slack algorithms do ``too much'' work, leading to very slow
convergence.  Also, caching does not speed up learning learning on this
dataset.
%
As on MNIST, the $1$-slack algorithm stops before the SZLJSP (in terms of
iterations) because of a tighter dual.  A detailed view is shown in
\Figref{ocr_small_dual} on the right.

>>>>

We start our experiments with the MNIST dataset.
The convergence of the primal suboptimality and training set loss in terms of
passes over the training set is shown in \Figref{mnist_curves}. While inference
is trivial, this is by far the largest dataset, making the $n$-slack algorithms
not feasible. We see that the stochastic algorithms are much faster than the
cutting plane algorithm, in particular initially, even in terms of iterations,
with the SZLJSP clearly leading the way.
Interestingly, the $1$-slack algorithm catches up near the desired
suboptimality.  Looking at the training set loss in \Figref{mnist_curves}
suggests that the high precision we demanded was not necessary, and we could
have terminated the stochastic algorithms much earlier.

@@

We now consider datasets with non-trivial inference.
The results for \textsc{OCR-small} are shown in \Figref{ocr_small_results}.
Considering the plot against passes over the dataset on the left, several
trends can be observed: the $n$-slack cutting plane algorithms converge
fastest, with the version that recomputes the QP at every step leading the
race. The algorithms are closely followed by the caching $1$-slack cutting
plane algorithm.  They are followed by the significantly slower SZLJSP
algorithm, and finally the non-caching $1$-slack cutting plane algorithm and
subgradient descent.  These results are intuitive, as they reflect ``how much
work'' each algorithm does for each loss-augmented prediction step. More work
towards the objective leads to faster convergence.  This ``more work'' is
quantified on the right hand side of \Figref{ocr_small_results}, where the suboptimality is plotted against time.
Clearly the $n$-slack algorithms do ``too much'' work, leading to very slow
convergence.  Also, caching does not speed up learning learning on this
dataset.

We want to highlight an interesting phenomenon here: The cutting-plane
algorithms stop immediately when reaching the desired suboptimality of $0.1$.
The SZLJSP algorithm, on the other hand, keeps on learning much longer---even
though the primal of the $1$-slack algorithms is always above the primal of the
SZLJSP\@. This is caused by a looser bound given by the dual. Remember that the
stopping criterion for both cutting-plane and SZLJSP are given by the duality
gap. It seems that while the primal objective converges much faster in the
SZLJSP algorithm than in the non-caching $1$-slack algorithm, the dual does
not. This means that in this practical experiment, the non-caching $1$-slack
algorithm was \emph{faster} in guaranteeing the desired suboptimality, and
therefore in terminating.  \Figref{ocr_small_dual} illustrates this point by
plotting primal and dual objectives for the $1$-slack cutting plane and the
SZLJSP algorithms. Taking a closer look, we find that the same behavior
occurred for MNIST, which is also shown in \Figref{ocr_small_dual}.
